Compiling refinement types to dependent types

### 2020-07-07 tex/paper.tex
Prepare reader for the slight notational abuse
Noticed one more case where the old-style subst is used

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic:
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq && \top																						  \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq && [| \nonterm G |] \land [| \{x/v\} \nonterm r |]  \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq && [| \nonterm r_1 |] \land [| \nonterm r_2 |]      \\
  & [| \nonterm{es}_1 = \nonterm{es}_2 |]                   && \triangleq && \text{oracle}(\nonterm{es}_1 = \nonterm{es}_2)   \\
\end{aligned}
\end{equation}

@@

$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)              \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}              \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))                      \\
  & \mu_\tau( \nonterm{es}_1 = \nonterm{es}_2 )                 && \triangleq \mu_\varepsilon(\nonterm{es}_1) \equiv \mu_\varepsilon(\nonterm{es}_2)  \\
%TODO add syntax/typing rules for True
  & \mu_\tau(B)                                                 && \triangleq B                                                                       \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements, being propositions about surface language terms equality,
    are translated to propositions stating the equality of translated core language terms,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}

>>>>

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic:
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq && \top																						  \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq && [| \nonterm G |] \land [| [ v \mapsto x ] \nonterm r |]  \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq && [| \nonterm r_1 |] \land [| \nonterm r_2 |]      \\
  & [| \nonterm{es}_1 = \nonterm{es}_2 |]                   && \triangleq && \text{oracle}(\nonterm{es}_1 = \nonterm{es}_2)   \\
\end{aligned}
\end{equation}

@@

$\mu_\tau$ is defined as follows,
with the slight abuse of notation to allow ``recursive'' calls
on refinement part of the surface language syntax:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)              \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}              \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))                      \\
  & \mu_\tau( \nonterm{es}_1 = \nonterm{es}_2 )                 && \triangleq \mu_\varepsilon(\nonterm{es}_1) \equiv \mu_\varepsilon(\nonterm{es}_2)  \\
%TODO add syntax/typing rules for True
  & \mu_\tau(B)                                                 && \triangleq B                                                                       \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements, being propositions about surface language terms equality,
    are translated to propositions stating the equality of translated core language terms,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}
